Lyman-$\alpha$ photons through rotating outflows

### 2018-03-30 paper/paper.tex
edit

In Table \ref{tab:values} we list the combination of \tauh,
\vrot and \vrot values used in this paper.
The range of values have some overlap with the expectations from a dwarf
galaxy with a total neutral hydrogen mass of $10^8$-$10^9$ $M_{\odot}$.
We run a total of $27$ different models.

\begin{table}
  \begin{center}
    \begin{tabular}{|c|c|c|}
      \hline
      \tauh & \vrot (\kms) & \vout (\kms) \\
      \hline
      \{$10^5$, $10^6$, $10^7$\}  & \{0, 50, 100\} & \{5, 25, 50\} \\
      \hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Parameters' Values.} List of values that were used
    to construct the radiative transfer models. Values in braces
    for a row indicate that all possible combinations in of
    \tauh, \vrot and \vout are used.}
  \label{tab:values}
\end{table}

@@

\section{Results}
\label{sec:results}

@@

Figure \ref{fig:standard_deviation} summarizes the standard deviation
results for all our models.
Each panel shows the STD as a function of \vrot. The black triangles
correspond to the full RT solution and the line to the DS
approximation.  
The optical depth increases from top to bottom and the outflow
velocity from left to right.
This quantitative plot confirms that the line width increases with
rotational velocity and  optical depth.
The DS successfuly reproduces all trends with the optical depth,
rotational velocity and outflow velocity.
However, the DS consistently underestimates the STD. 
The difference between the RT and DS increases with the outflow
velocity and the rotational velocity, and decreases with increasing
optical depth.
In the range of parameter space explore, this difference has as an
upper bound of $\sim 7\%$, $3\%$ and $\sim 2\%$ for
 $\tauh=10^5$, $10^6$ and $10^7$, respectively.

@@

>>>>

In Table \ref{tab:values} we list the combination of \tauh,
\vrot and \vrot values used in this paper.
The range of values have some overlap with the expectations from a
galaxy with a total neutral hydrogen mass of $10^8$-$10^9$
$M_{\odot}$. We run a total of $27$ different models.

@@

\section{Results}

\label{sec:results}

@@

Figure \ref{fig:standard_deviation} summarizes the standard deviation
results for all our models.
Each panel shows the STD as a function of \vrot.
All panels were computed using a viewing angle of $\theta =
90^{\circ}$ (perpendicular to the rotation axis), which has the most
extreme ifluence from rotation.
 The black triangles
correspond to the full RT solution and the line to the DS
approximation.  
The optical depth increases from top to bottom and the outflow
velocity from left to right.
This quantitative plot confirms that the line width increases with
rotational velocity and  optical depth.
The DS successfuly reproduces all trends with the optical depth,
rotational velocity and outflow velocity.
However, the DS consistently underestimates the STD. 
The difference between the RT and DS increases with the outflow
velocity and the rotational velocity, and decreases with increasing
optical depth.
In the range of parameter space explore, this difference has as an
upper bound of $\sim 7\%$, $3\%$ and $\sim 2\%$ for
 $\tauh=10^5$, $10^6$ and $10^7$, respectively.

@@

Figure \ref{fig:bimodality} shows the results for the bimodality using
the same layout as in the two previous Figures.
